The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-22 Writeup/paper_v3.tex
Fig 6 comments and tweaks to associated text

% \rachel{As we discussed, you should get rid of the early parts of this
%   regarding second moments, and replace it with a brief description of
%   what shape estimates we use from GalSim (re-Gaussianization).}
% 
% {\bf Should explain in brief Claire's work.} \\
\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{sample_histograms}
 \caption{The distributions of the morphological parameters of interest, namely the distortion, \sersic index and \btt are presented. 
          The shape of the distribution depends on the way the volume-limiting process is carried out. \s$0$ refers to the flux-limited ($m_\text{F814}\le23.5$) sample
          and \s$1$, \s$2$ and \s$3$ refer to the volume-limited samples, as discussed in Sec.~\ref{sub:volumelimiting}}
  \label{fig:sample_histograms}
\end{figure*}

@@

\arun{New paragraph:} Fig.~\ref{fig:sample_histograms} show the distribution of these morphological and shape parameters for the flux-limited sample \s$0$ and the various
volume-limited samples - \s$1$, \s$2$ and \s$3$. It is important to understand the biases in selecting the galaxies in each of the volume-limiting process to be able to interpret the results.
For instance, galaxies with lower \sersic indices are preferentially selected in \s$2$ when compared to \s$1$ and \s$3$. And similarly, galaxies with low ellipticity/distortion values
are rejected in generating \s$2$ and \s$3$ while they are retained in \s$1$.

>>>>

% \rachel{As we discussed, you should get rid of the early parts of this
%   regarding second moments, and replace it with a brief description of
%   what shape estimates we use from GalSim (re-Gaussianization).}
% 
% {\bf Should explain in brief Claire's work.} \\
\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{sample_histograms}
 \caption{The distributions of the morphological parameters of interest, namely the distortion, \sersic index and \btt are presented. 
          The shape of the distribution depends on the way the volume-limiting process is carried out. \s$0$ refers to the flux-limited ($m_\text{F814}\le23.5$) sample
          and \s$1$, \s$2$ and \s$3$ refer to the volume-limited
          samples, as discussed in
          Sec.~\ref{sub:volumelimiting}. \rachel{I am confused by the
            top line: first, distortion is $(1-q^2)/(1+q^2)$, not
            $(1-q)/(1+q)$.  Second, I am not sure which shapes you are
          plotting - from Claire or from re-Gaussianization.  It seems
        redundant to have two plots of the same thing, so I hope that
        one is from Claire and one from re-Gaussianization, but these
        needs to be indicated clearly.  Finally, we have the option of
      deliberately plotting different things (like $q$ from Claire
      vs. distortion from re-Gaussianization) or explicitly choosing
      to plot the same thing (like total distortion from Claire
      vs. total distortion from re-Gaussianization).  I'm not sure
      which is best; the latter would allow a comparison between the
      two types of shape estimates, which could be interesting, so I'm
      inclined to say you should do that.}}
  \label{fig:sample_histograms}
\end{figure*}

@@

Fig.~\ref{fig:sample_histograms} shows the distribution of these morphological and shape parameters for the flux-limited sample \s$0$ and the three
volume-limited samples - \s$1$, \s$2$ and \s$3$. In addition to the
basic value in characterizing these distributions for our sample
overall, it is also useful to understand how the samples change when
we vary our method of volume-limiting the sample.
For instance, galaxies with lower \sersic indices are preferentially
selected in \s$2$ compared to \s$1$ and \s$3$. Similarly, galaxies
with low ellipticity/distortion values 
are rejected in generating \s$2$ (despite the lack of any explicit
cut on shapes) while they are retained in
\s$1$ and \s$3$.  A simple explanation is that the cuts in \s$2$ are
preferentially removing early-type populations, which have higher
\sersic indices and lower ellipticities.  For example, if the
luminosity evolution that was adopted is too strong particularly for
early type populations, that could give rise to the effect shown in
Fig.~\ref{fig:sample_histograms}.
